---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# `kbodatamining`

## Package Introduction

The goal of `kbodatamining` package is analizing and visualizing korean baseball data(KBO data). 
This package is intended to make use of KBO data collected from Python to R.

## Package Installation

You can install package `kbodatamining` from github with the following command.
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("choosunsick/kbodatamining")
```

## Package Functionality
There are two primary functions in this package. The first is to make the records of players box-score.
for example:

```{r}
library(kbodatamining)

# batter example
batter_boxscore(data = hanhwa_batter_2018,name = "이용규",yearly = 2018)
# pitcher example
pitcher_boxscore(data = hanhwa_pitcher_2018,name = "정우람",yearly = 2018)
# team hitting example
team_batter_boxscore(data = hanhwa_batter_2018,teamname = "한화",yearly = 2018)
# team pitching example
team_pitcher_boxscore(data = hanhwa_pitcher_2018,teamname = "한화",yearly = 2018)
```

The second is to visualize monthly or seasonal comparisons for each player. In addition, these two functions can be applied to each team.
for example:
```{r}
library(kbodatamining)
theme_set(theme_gray(base_family = "AppleGothic"))
# comparing batters
oneseason_batter_compare(data = hanhwa_batter_2018,playername1 = "이용규",playername2 = "정근우",yearly=2018)
# comparing pitchers
oneseason_pitcher_compare(data = hanhwa_pitcher_2018,playername1 = "정우람",playername2 = "송은범",yearly=2018)
# comparing batters of team
compare_batter_statistic_teams(hanhwa_batter_2018,"한화","LG",yearly=2018)
# comparing pitchers of team
compare_pitcher_statistic_teams(hanhwa_pitcher_2018,"한화","LG",yearly=2018)
```

You can find a detailed explanation of this function in the 'plotting example' document of the vignette folder.

## Notes on data
How to collect KBO data from Python can be found at [LINK](https://choosunsick.github.io/post/kbo_data_wrangling/).
For reference, the sample data in the package includes the data of 2018 season Hanhwa team. This sample data is divided into 'hanhwa_batter_2018', 'hanhwa_pitcher_2018'. You can check the package's functions using sample data.

## Json data processing (json data 처리과정)

If you see the link above and get a json file for the KBO game through Python, you will have to process the json file to use it in R. So I'll show you an example of loading a json file from R and making it to DATAFRAME. An example of the process will be shown through the data in the json_sample folder in this github.
for example:

```{r}
library(jsonlite)
library(kbodatamining)
# read json file
sample_set <- fromJSON("./json_sample/Hanhwa_normalseason_2018.json")
# make batter data dataframe 
# If you want pitch data, use json2pitcherdf instead of json2batterdf
hanhwa_batter_2018 <- do.call(rbind,lapply(names(sample_set),FUN = function(x)json2batterdf(sample_set,x)))
# organizing column order & column name
hanhwa_batter_2018 <- hanhwa_batter_2018[,c(18:21,11,16:17,1:9,24,23,22,13,12,10,15)]
colnames(hanhwa_batter_2018) <- c('date','away','home','doubleheader','name','team','position',
                                  'one','two','three','four','five','six','seven','eight','nine',
                                  'ten','eleven','twelve','ab','h','r','rbi')
head(hanhwa_batter_2018)
```

In addition, you need to create an id column of the players.

```{r}
library("kbodatamining")
# read id list 
batter_id  <- read.csv("./player_id_list/batter_id_list.csv",stringsAsFactors = F)
# extract the appropriate id list for your data
batter_id_2018 <- batter_id[substr(batter_id$date,1,4)==2018,]
batter_id_hanhwa_2018 <- batter_id_2018[batter_id_2018$away=="한화"|batter_id_2018$home=="한화",]
# make id column 
hanhwa_batter_2018 <- get_player_id(hanhwa_batter_2018,batter_id_hanhwa_2018)
head(hanhwa_batter_2018)
```

Repeat the above process with your json file, changing only the year and team name.
