---
title: "kbodatamining manual"
author: "Sunsick Choo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This document describes the plot functions that this package has.
(이 문서에서는 이 패키지가 가지고 있는 플로팅 기능에 대해 설명할 것입니다.)

## oneseason_compare_batter function   
(첫번째는 타자들을 비교하여 plot을 그려주는 함수입니다.)
This function is a function that draws a plot comparing the hitters. 
이 함수의 return값은 선수의 여러 스탯을 2개의 plot으로 나누어 그려줍니다.
The return value of this function divides the player's statistics into two plots.
첫 번째는 홈런,안타,득점 등과 같은 스텟을 비교하는 플롯입니다.
The first is a plot that compares stats, such as home runs, hits, and scoring.
두 번째는 타율,장타율,출루율 같은 스텟을 비교하는 플롯입니다.
The second is a plot that compares stats, such as batting average, slugging percentage, and on-base percentage.
이 함수에는 'yearly', 'monthly' 인자가 있습니다. 이 인자들에 적합하지 않은 값을 넣을 경우 에러가 발생합니다.
This function has a 'yearly', 'monthly' parameter. If you put a value that is not suitable for these parameters, an error occurs.
예를 들면 데이터에 없는 선수를 비교하려하거나 데이터에 없는 시즌을 비교하려고 할 때 에러가 발생합니다.  
For example, an error occurs when you try to compare a player or a season that is not in the data.


## oneseason_compare_pitcher function
This function is a function that draws a plot comparing the pitchers. 


## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
